FraCaS: Temporal Analysis

### 2020-06-09 paper2020/paper.tex
formatting
blurb on progressive

\paragraph{time references and aspectual classes}

@@

@@

Another issue to be looking at is the codification of lexical aspect. In what we have been doing so far, we did not distinguish between the present continuous and the present or the simple past and the past continuous and their interaction with non-lexical aspect.  The main reason for this  is that in the test suite, even though there are examples of inferences based on the either lexical or non-lexical aspect, no example where an interaction between the two exists. For example, one such case is the one shown below and exemplifies the difference between activities and accomplishments with respect to the different inferences they give when used  in the past continuous:

@@

% \bibliography{../PaperTools/bibtex/jp}
% Things we cannot handle (I think): John was writing a book in 1991 -> John wrote a book in 1991 (I think we predict entailment here). This is because there is no distinction with progressive and non progressive aspect. We did not do it, I guess because it was needed, but just for future reference. There are similar examples playing around with LEXICAL aspect (aspect grammatically encoded) that we could look at in future work
% Accomplishments usually involve a culmination point in the action which is necessary for the event to be completed. This is not necessary for activities. John stopped writing a book not-> John wrote a book (but does imply that John was writing a book), but, John stopped running -> John run and John was runnning 
\end{document}

>>>>

\paragraph{Time references and aspectual classes}

@@

\paragraph{Progressive aspect}

We treat verbs in the progressive form as different semantically. For
example, ``John was writing a book'' is encoded as
$∃t1, t2. t1<= t2, t2 <= now, PROG_write(John,book,t1,t2)$, while
``John wrote a book'' is encoded as
$∃t1, t2. t1<= t2, t2 <= now, write(John,book,t1,t2)$. This is
necessary, because $PROG_write$ is subject to
$\constant{subsumption}$: if John is writing in interval $[t1,t2]$
then he is writing in any subinterval. However, the same cannot be
said of $write$: the end-points of the interval indicates the time
needed to complete the achievement. (For example, John wrote a book in
1993 does not entail John wrote a book in March 1993.) Thus, $write$
is on the contrary subject to $\constant{unicity}$. Finally, we also
have $write(x,y,t1,t2) -> PROG_write(x,y,t1,t2)$. That is, the
achievement variant implies the stative variant, in the same interval.
Consequently we get the entailment from ``John wrote a book'' to
``John was writing a book''.

Finally we note that not all verbs are subject to the
stative/achievement distinction induced by the progressive. For
example, the phrases ``John ran'' and ``John is running'' appear to be
logically equivalent, for our purposes\todo{For the FraCaS suite?}.

@@

Another issue to be looking at is the codification of lexical
aspect.\todo{update} In what we have been doing so far, we did not distinguish
between the present continuous and the present or the simple past and
the past continuous and their interaction with non-lexical aspect.
The main reason for this is that in the test suite, even though there
are examples of inferences based on the either lexical or non-lexical
aspect, no example where an interaction between the two exists. For
example, one such case is the one shown below and exemplifies the
difference between activities and accomplishments with respect to the
different inferences they give when used in the past continuous:

@@

% \bibliography{../PaperTools/bibtex/jp}

% Things we cannot handle (I think): John was writing a book in 1991
% -> John wrote a book in 1991 (I think we predict entailment
% here). This is because there is no distinction with progressive and
% non progressive aspect. We did not do it, I guess because it was
% needed, but just for future reference. There are similar examples
% playing around with LEXICAL aspect (aspect grammatically encoded)
% that we could look at in future work

% Accomplishments usually involve a culmination point in the action
% which is necessary for the event to be completed. This is not
% necessary for activities. John stopped writing a book not-> John
% wrote a book (but does imply that John was writing a book), but,
% John stopped running -> John run and John was runnning

\end{document}
